Kyoto VR MQP Paper First Draft

### 2019-09-20 paper.tex
fix prof. cuneo's suggestions
Accepted suggestions from Professor Cuneo's Sep 9 comments. Mostly removing
commas.

Before our project started, Kyoto VR was already using an app with a limited
form of AR for tours. The app, called izi.TRAVEL, allows users to create audio
tours with audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel}, but can be used for tours
of historic sites too.  Kyoto VR used the platform to make an audio tour of
Kinkaku-ji, one of the most popular tourist destinations in
Japan~\autocite{bornoff2000} and an important historic heritage
site~\autocite{unesco}.

@@

ARKit 3 aims to support a wide array of new features, and will be available in
iOS 13. Notably, one of these features is ``people occlusion,'' which will allow
virtual objects to be realistically obscured when someone walks in front of the
object~\autocite{apple2019}. This kind of technology could be useful for us
since our app uses AR in crowded places.  As of August, 2019, this feature is
not on the horizon for Google's Android AR framework, ARCore.

@@

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware.  Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware [citation needed about
emulator inaccuracies]. Secondly, and most importantly for AR, it is common for
emulation to be much slower compared to real hardware. In a question submitted
to \textit{Compute!} magazine asking whether it is possible for a Commodore 64
to emulate MS-DOS, the editor responded ``Yes, it's possible for a 64 to emulate
an IBM PC, in the same sense that it's possible to bail out Lake Michigan with
a teaspoon.'' The editor goes on to explain ``Emulation is a complex business,
but here's one rule of thumb: The only way to successfully emulate a machine is
with a much more powerful machine''~\autocite{warick1988}. In our case,
emulating Android on a desktop operating system is closer to emulating a C64 on
an IBM PC running MS-DOS (rather than the other way around, thankfully.) The
moral is that the speed problem facing emulators is just as real as it was in
1988. Considering that AR already pushes modern phone harware to the limit,
emulation is not something is not something we wanted to struggle with. On top
of this, our testing required us to move the camera through the world at
various speeds and angles, which is simply cumbersome with a webcam and laptop.

ViroReact offers a convenient ``test bed'' for rapidly testing your ViroReact
app on native hardware without the need for an emulator. In the root directory
of your project, you can launch a Node server with the command \texttt{npm
start}. From here, you can input the provided URL into the Viro Media app. This
will quickly download the code, graphics and 3D object files from the server
and launch a functional version of the app \autocite{viro-testbed2019}. This
allowed us to get a real AR app up and running on our devices much more easily
than any of the other frameworks/engines we explored. Unfortunately, the test
bed app was somewhat unreliable based on our experience; the test bed would
frequently crash, or would not be able to download the files from the Node
server. The most reliable way to test our app was to compile a binary and
manually install it onto our devices, which completely defeats the purpose of
the test bed app.

@@

Our backend allows users to save their tours to our server, and load those same
tours back into the editor to resume work.  The geographic area of each region
can be adjusted by clicking and dragging. Vertices can also be added and
deleted if the needs of the tour change over time.

@@

Within each object in the region list, we can see that the region has four
properties: a name, a list of coordinates, a list of audio files, and a list of
multiple image files. (In the current design of the app, it only makes sense to
associate one audio file per region, but the format makes it easy to
accommodate for multiple audio files in the future.) One disadvantage is that
all media files have to have unique names. This is because the zip that is
created by the editour backend contains all of the media files in a flat file
structure. The above JSON is used to associate each media file with a region,
meaning that the filename needs to act as a primary key. The backend will
respond with a message if this is the case, prompting the user to have unique
names for all files.

>>>>

Before our project started, Kyoto VR was already using an app with a limited
form of AR for tours. The app, called izi.TRAVEL, allows users to create audio
tours with audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel} but can be used for tours
of historic sites too.  Kyoto VR used the platform to make an audio tour of
Kinkaku-ji, one of the most popular tourist destinations in
Japan~\autocite{bornoff2000} and an important historic heritage
site~\autocite{unesco}.

@@

ARKit 3 aims to support a wide array of new features and will be available in
iOS 13. Notably, one of these features is ``people occlusion,'' which will allow
virtual objects to be realistically obscured when someone walks in front of the
object~\autocite{apple2019}. This kind of technology could be useful for us
since our app uses AR in crowded places.  As of August 2019, this feature is
not on the horizon for Google's Android AR framework, ARCore.

@@

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware.  Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware [citation needed about
emulator inaccuracies]. Conversely, errors that exist in the hardware version
may not appear in the emulation. Secondly, and most importantly for AR, it is
common for emulation to be much slower compared to real hardware.

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way to
successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The moral is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone harware to the limit, emulation is not something is
not something we wanted to struggle with. On top of this, our testing required
us to move the camera through the world at various speeds and angles, which is
simply cumbersome with a webcam and laptop.

ViroReact offers a convenient ``test bed'' for rapidly testing your ViroReact
app on native hardware without the need for an emulator. In the root directory
of your project, you can launch a Node server with the command \texttt{npm
start}. From here, you can input the provided URL into the Viro Media app. This
will quickly download the code, graphics, and 3D object files from the server
and launch a functional version of the app \autocite{viro-testbed2019}. This
allowed us to get a real AR app up and running on our devices much more easily
than any of the other frameworks/engines we explored. Unfortunately, the test
bed app was somewhat unreliable based on our experience; the test bed would
frequently crash or would not be able to download the files from the Node
server. The most reliable way to test our app was to compile a binary and
manually install it onto our devices, which completely defeats the purpose of
the test bed app.

@@

Our backend allows users to save their tours to our server and load those same
tours back into the editor to resume work.  The geographic area of each region
can be adjusted by clicking and dragging. Vertices can also be added and
deleted if the needs of the tour change over time.

@@

Within each object in the region list, we can see that the region has four
properties: a name, a list of coordinates, a list of audio files, and a list of
multiple image files. (In the current design of the app, it only makes sense to
associate one audio file per region, but the format makes it easy to
accommodate for multiple audio files in the future.) One disadvantage is that
all media files have to have unique names. This is because the zip that is
created by the Editour backend contains all of the media files in a flat file
structure. The above JSON is used to associate each media file with a region,
meaning that the filename needs to act as a primary key. The backend will
respond with a message if this is the case, prompting the user to have unique
names for all files.
